Group 9 Paper

### 2021-12-16 paper.Rmd
added reprtree code without output, still missing installation for now.

```{r,echo=FALSE}
rf_fit <- randomForest(as.factor(HeartDisease) ~ ., data = train, mtry = sqrt(ncol(train)), importance = TRUE, type= "classification", ntrees=1000)

@@

Next, we fitted a Random Forest, in this case I chose the number of predictors randomly sampled at each iteration to be $m=\sqrt{p}$, as this was what was recommended by the class book. For random forests, the test accuracy relatively good at 0.8664 which is good, but not better than some of te other methods. Looking at the variable importance, we have some similar results to the other tree based methods, as ST_Slope, ChestPainType, and Cholesterol seem to be the most important variables. However, in random forests we got a negative value for the RestingBP, which is somewhat consistent with the other methos as RestingBP also did not seem to be a important variable in dertermining heart disease, however, in this case it means that for random forests is seems that including RestingBP decreases the accuracy of the method.

@@

>>>>

```{r,echo=FALSE}
set.seed(445)

rf_fit <- randomForest(as.factor(HeartDisease) ~ ., data = train, mtry = sqrt(ncol(train)), importance = TRUE, type= "classification", ntrees=1000)

@@

Next, we fitted a Random Forest, in this case I chose the number of predictors randomly sampled at each iteration to be $m=\sqrt{p}$, as this was what was recommended by the class book. For random forests, the test accuracy relatively good at 0.8719 which is good, but not better than some of te other methods. Looking at the variable importance, we have some similar results to the other tree based methods, as ST_Slope, ChestPainType, and Cholesterol seem to be the most important variables. However, in random forests we got a negative value for the RestingBP, which is somewhat consistent with the other methos as RestingBP also did not seem to be a important variable in dertermining heart disease, however, in this case it means that for random forests is seems that including RestingBP decreases the accuracy of the method.

@@

{r fig.height=7, fig.width=15, message=FALSE, warning=FALSE,echo=FALSE}
set.seed(445)

reptree <- ReprTree(rf_fit, train, metric='d2')

plot(reptree, index=1)

In the tree we can see ST_Slope is the root node, which was expected since most models considered it the most important variable, however, it is interesting that in the next nodes we have FastingBS and Sex:F both variables were not considered very important by the random forest model. This made us somewhat skeptical about this algorithm, however, it does make sense as we are looking for a representative tree not the most accuracate tree, if we had more time we would've liked to implement our own algorithm based of the paper in order to further validate the results.
